A Gentle Introduction to Structural Causal Models

### 2021-05-16 scm.Rmd
scm stuff

@@

- Machine learning has provided many insights into different research problems 
- One issue is the consideration of 'What are we actually predicting'?
- Mainstream tools are build on association-based learning 
- Associations are not enough for high stake settings 
- In disciplines like psychology or economics people are less interested in associational learning
- We want causation and not correlation

@@

>>>>

# Motivation

```{r, out.width= "70%", out.height = "70%", fig.align='center'}
library(knitr)
setwd("~/Desktop/SOSE2021/causal_ml")
include_graphics('./images/correlation.jpg')
```

@@

- Machine learning has provided many insights into different problems 
- One issue is the consideration of 'What are we actually predicting'?
- Mainstream tools are build on association-based learning 
- Associations are not enough for high stake settings 
- In disciplines like psychology or economics people are less interested in associational learning
- We want causation and not correlation

@@

# Table of Contents

* Foundations of SCMs 
  * Assumptions 
  * Comparative Causal Tools 
  * Historical Development 
* Pearl's Causal Hierachy 
  * prediction 
  * intervention 
  * Counterfactuals 
  * Implications 
* Graphical Models 
  * Features 
  * Implications
* Causality and Time
